Case study validations of automatic bullet matching

### 2018-10-25 index.Rmd
comment out a comment, add one of my own

\hh{XXX error rates on land to land matches? ROC curves in \autoref{fig:rocs} and corresponding AUC results for all studies in \autoref{tab:aucs} XXX}

>>>>

<!-- \hh{XXX error rates on land to land matches? ROC curves in \autoref{fig:rocs} and corresponding AUC results for all studies in \autoref{tab:aucs} XXX} -->

\svp{XXX show ROC for bullet-to-bullet is perfect, just for emphasis?}
